Cosmic web correlations with the shape, spin and peculiar velocties of dark matter halos

### 2013-10-23 paper/main.tex
adding some text to the introduction

\documentclass[usenatbib]{mn2e} 
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{epsfig}  
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}
% To highlight comments 
\usepackage{color}
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}
\definecolor{blue}{rgb}{0.1,0.3,0.9}
\newcommand{\blue}{\color{blue}}

@@

%-------

\section{Theoretical Antecedents}
\label{sec:theory}

@@

... Table 1 and Table 2 summariz recent results found in the literature for
shape and angular momentum alignment, respectively.

@@

\cite{Libeskind2013} & V-Web & $1 \hMpc$ & 
filament &$++$ & $>10^{12}$\hMsun\\
&   & & 
filament &$+$ & $<10^{12}$\hMsun\\
&   & & 
wall & $++$ & all masses\\

@@

& &  & 
filament & $+$ & $<10^{12}\hMsun$\\

@@

\end{tabular}\\
\caption{Summary of previous theoretical results.
Shape. Indicates the alignment of the halo's major axis along a
filament or a sheet.} 
\end{table*}

@@

@@

&   & & 
wall & $++$ & all masses\\

\cite{Trowland2013} & Hessian density & $2-5\hMpc$ & 
filament & $-$ & $> 5\times 10^{12}$\hMsun\\
&   & & 
filament & $+$ & $< 5\times 10^{12}$\hMsun\\

@@

& & & 
wall & $++$ & all masses\\

@@

& &  & 
filament & $--$ & only if correlated with shape\\

@@

& & - &
filament& $-$ & $>10^{12}$\hMsun\\

& & - &
filament& $+$ & $<10^{12}$\hMsun\\

@@

\end{tabular}
\caption{Summary of previous theoretical results.
Angular Momentum}
\end{table*}

>>>>

\documentclass[usenatbib]{mn2e} 
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{epsfig}  
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}

% To highlight comments 
\usepackage{color}
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}
\definecolor{blue}{rgb}{0.1,0.3,0.9}
\newcommand{\blue}{\color{blue}}

@@

The formation of large scale structure in the Universe proceeds by
gravitational instability. This is an intrinsic anisotropic
process. [Pancake formation ...]

Numerical simulations allow the exploration of a deep nonlinear
regime, following the formation of virialized dark matter halos, which
host observable galaxies. Some characteristics of these halos have to
be linked to the environment in which they formed. One way to studty
the connection halo-environment is to quantify the degree of
correlation between different halo properties and their surrounding
density and velocity fields.

Among the properties that are of interest we find the shape, spin and
peculiar velocity. [Relevanc of dark matter halo shapes ...]
[Relevance of halo spin ...] [Relevance of peculiar velocities]

There is large tradition of theoretical precedents for the
measurements of shape and spin alignment. In this \documentname we
review most of these studyes and offer our own study with
complementary numerical techniques and simulations. [Brief summary of
  the appendix ...]

We also present the results for the alignment of peculiar velocities
with large scale structure. Such a study has received less atention in
the literature. However, we consider that it presents relevant
insights for the study of cosmic flows.

The structure of this \documentname is the following.

\section{Theoretical Precedents}
\label{sec:theory}

@@

... Table 1 and Table 2 summarizes recent results found in the literature for
shape and angular momentum alignment.

@@

{\bf Contreras et al. (2014)} & T-Web & $0.5-1 \hMpc$ & 
filament &$?$ & $>10^{12}$\hMsun\\
&   & & 
filament &$?$ & $<10^{12}$\hMsun\\
&   & & 
wall & $?$ & all masses\\\hline

{\bf Contreras et al. (2014)} & Vp-Web & $0.5-1 \hMpc$ & 
filament &$?$ & $>10^{12}$\hMsun\\
&   & & 
filament &$?$ & $<10^{12}$\hMsun\\
&   & & 
wall & $?$ & all masses\\\hline

\cite{Libeskind2013} & V-Web & $1 \hMpc$ & 
filament &$++$ & $>10^{12}$\hMsun\\
&   & & 
filament &$+$ & $<10^{12}$\hMsun\\
&   & & 
wall & $++$ & all masses\\\hline

@@

& &  & 
filament & $+$ & $<10^{12}\hMsun$\\\hline

@@

\end{tabular}\\
\caption{Shape alignment with the cosmic web. Summary of theoretical
  results provided by methods comparable to ours.}
\end{table*}

@@

{\bf Contreras et al. (2014)} & V-Web & $1 \hMpc$ & 
filament &$?$ & $>10^{12}$\hMsun\\

&   & & 
filament &$?$ & $<10^{12}$\hMsun\\

&   & & 
wall & $?$ & all masses\\\hline

{\bf Contreras et al. (2014)} & Vp-Web & $1 \hMpc$ & 
filament &$?$ & $>10^{12}$\hMsun\\

&   & & 
filament &$?$ & $<10^{12}$\hMsun\\

&   & & 
wall & $?$ & all masses\\\hline

@@

&   & & 
wall & $++$ & all masses\\\hline

\cite{Trowland2013} & Hessian density & $2-5\hMpc$ & 
filament & $-$ & $> 5\times 10^{12}$\hMsun\\
&   & & 
filament & $+$ & $< 5\times 10^{12}$\hMsun\\\hline

@@

& & & 
wall & $++$ & all masses\\\hline

@@

& &  & 
filament & $--$ & only if correlated with shape\\\hline

@@

& & - &
filament& $-$ & $>10^{12}$\hMsun\\\hline

& & - &
filament& $+$ & $<10^{12}$\hMsun\\\hline

@@

\end{tabular}
\caption{Spin alignment with the cosmic web. Summary of theoretical
  results provided by methods comparable to ours.}

\end{table*}
